Predicting the conformational preferences of proteins using a physics-based free energy method

### 2013-05-16 Paper/paper.tex
Sarina's changes

Understanding the free energy differences between different conformations of a protein is important for
understanding biochemical mechanisms. The calculation of such free energy differences is difficult and
computationally demanding. In this work, we explore the use of the "confinement method'' to calculate free energy
differences between conformations. This method provides two main advantages: (1) it does not require a reaction
coordinate or transition path, and (2) it is fast to compute. The free energy difference can be approximately decomposed
into per-residue contributions, providing insight into the physical basis for the preference of one conformation
over another. We show that the confinement method can correctly predict the conformational preferences of chameleon
sequences (nearly identical sequences with different structures); can identify the most native-like structures produced
by structure prediction algorithms; and can yield detailed insight into the mechanisms behind these preferences.

>>>>

Understanding the free energy differences between different conformations of a protein is important for
understanding biochemical mechanisms. The calculation of such free energy differences is difficult and
computationally demanding. In this work, we explore the use of the "confinement method'' to calculate free energy
differences between conformations. This method provides two main advantages: (1) it does not require a reaction
coordinate or transition path, and (2) it is fast to compute. The free energy difference can be approximately composed
into per-residue contributions, providing insight into the physical basis for the preference of one conformation
over another. We show that the confinement method can correctly predict the conformational preferences of chameleon
sequences (nearly identical sequences with different structures); can identify the most native-like structures produced
by structure prediction algorithms; and can yield detailed insight into the mechanisms behind these preferences.
